### 2016-11-10 datamining/summery.tex
Freq pattern mining

\documentclass[9pt,landscape]{extarticle}
\usepackage{multicol}
\usepackage{calc}
\usepackage{ifthen}
\usepackage[landscape]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{color,graphicx,overpic}
\usepackage{hyperref}
\usepackage{graphicx}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\vDash$}}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

@@

>>>>

\documentclass[8pt,landscape]{extarticle}
\usepackage{multicol}
\usepackage{calc}
\usepackage{ifthen}
\usepackage[landscape]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{color,graphicx,overpic}
\usepackage{hyperref}
\usepackage{graphicx}
\newcommand{\indep}{\rotatebox[origin=c]{90}{$\vDash$}}
\usepackage{amssymb}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

@@

A node labled graph is a quadruple $G=(V,E,\Sigma,L)$ where: $V$ is the set of
nodes, $E$ is the set of edges, $\Sigma$ is the set of labels, and $\L: V->
\Sigma$ is a labeling function.
A labeled rooted unordered tree $U = (V , E , \Sigma, L, v^r )$ is an $G$ with a
special node $v^r$ called the root of the tree such that there exists exactly
one path betweeen the root node and any other node in $V$.
A labeled rooted rodered tree $T = (V, E, L, v^r, \leq)$ is an unordered tree
$U$ where between all the iblings an orderer $\leq$ is dfined. to every node in
an ordered tree a preorder $(pre(v))$ number is assigned according to the depth
first traversel of the tree.
\subsubsection{Tree inclusion relations}
An induced subtree preserves parent child relationships.
$\pi(v)$ denotes the parent of node $v$.
Given two oreered trees $D$ and $T$ we call $T$ an induced subtree of $D$ if
there exists an injective matching function $\phi$ of $V_T$ into $V_d$ with the
following conditions: $\phi$ preservers the labels: $L_T(v)=L_D(\phi(v))$,
$\phi$ preservers the parent child relation:
$v_i = \pi_T(v_j)\Leftrightarrow \phi(v_i)=\pi_D(\phi(v_j))$
$\phi$ preservers the left to right orderbetween the nodes: $pre(v_i) <
pre(v_j ) \Leftrightarrow pre(\phi(v_i)) < pre(phi(v_j))$  
An induced subtreee $T$ can be obtained from a tree $D$ by rpeatedly removing
leaf nodes, or possibly the root node if it has only one child.
This definition is the same for embedded subtree, except the equal sign become
$\in$ in the relation constiant and $\pi$ talks about the ancestor set.
An embedded subtree preserves ancestor decendent realtionships. 
\subsubsection{Freq tree mining task}
Given a database of trees $D=\{d_1, d_2, \dots, d_n\}$ and a tree inclusion
relation $\preceq$ we define the suppot of a tree $T$ as
$sup(T,D)=|\{d\in D | T \preceq d\}|$. Given a minimum support treshehold
minsup, compute $\mathcal{F}(minsup,D)=\{T|sup(T,D)\leq minsup\}$
\emph{Anti monoticity property}: For a database of trees $D$ and two trees $T_1$
and $T_2$ we have $T_1 \preceq T_2 \Rightarrow sup(T_1, D) \leq sup(T_2, D)$,
because $\forall d \in D: T_2 \preceq d \Rightarrow T_1 \preceq d$
Hence in a level wise search fro frequenttreees there is no point in expanding
infrequent trees.
\subsubsection{Right most extension}
Let $T_k$ denote a tree of size $k$.
Consider the node numbering of $T_k$ according to pre-order (depth-first)
traversal of the tree.
The right-most branch of the tree is the path from the root node to the
right-most leaf (i.e. the node with number $k$).
To expand the tree $T_k$,
it is only allowed to add a node as the right-most child of a node on
the right-most branch of $T_k$.
This node gets number $k + 1$,
as it is the last node in the pre-order traversal of $T_{k+1}$.
The right-most extension technique generates each tree at most once.
Also, the right-most expansion technique generates every possible tree, so each
tree is generated exactly once.
\emph{occurene list}:
To determine whether a pattern tree occurs in a data tree, an occurrence list
is maintained that contains the list of nodes in the data tree to which the
nodes in the pattern tree can be mapped.
FREQT only stores the nodes of the data tree to which the right-most node in
the pattern tree can be mapped.
This is sufficient since only the nodes on the right-most branch are needed
for future extension.
\subsection{Frequent pattern and clasification}
Frequent pattern mining can also be used to extract features for classification
tasks: 1 Find frequent patterns per class.
2 Define discriminating patterns, for example,
as patterns that are frequent in one class but not in the other.
3 Use the presence/absence of such a discriminating pattern as a (binary)
feature for constructing a classifier (e.g. classification tree!).
4 In this way we can include non-tabular data (sequences, trees, graphs)
into an algorithm that requires a tabular data structure.
